Document Knowledge Base Linking for Information Retrieval

### 2016-05-15 paper.tex
fix some formatting, one rewording

These links enrich documents by connecting knowledge base information such as hyperlink graphs, entity membership in categories, and additional text to the annotated documents. Information retrieval (IR) systems may reasonably expect to be able to use this valuable data to improve the quality of search results. Unfortunately, producing high quality entity annotations is often a computationally expensive process. In addition, these systems generally require training data, which increases the barrier to use. Much entity linking and wikification research has also assumed more amenable circumstances that complicate their application to real-world text. For example, until 2014, the KBP entity linking track supplied explicit mention boundaries to participants.

@@

\noindent Like $P(q_i|D)$, we estimate $P(q_i|E)$ as a Dirichlet-smoothed query likelihood, but using the description text for entry $E$ to estimate of the underlying model. By virtue of our entity-document scoring and normalization, we also have $P(E|D)$.

\begin{figure*}[!htb]
\centering
\begin{subfigure}{\columnwidth}
\centering
\includegraphics[width=.9\columnwidth]{figures/sweep-entities-AP.pdf}
\end{subfigure}%
\begin{subfigure}{\columnwidth}
\centering
\includegraphics[width=.9\columnwidth]{figures/sweep-entities-robust.pdf}
\end{subfigure}
%\begin{subfigure}{.5\columnwidth}
%\centering
%\includegraphics[width=\columnwidth]{figures/sweep-stanbol.pdf}
%\caption{Stanbol}
%\end{subfigure}
\caption{Sweeps over values of $\lambda$ for AP (a) and robust (b) \textit{kb} runs. $\lambda=0.0$ is the baseline run scored only on the document text, while $\lambda=1.0$ is based entirely on the entity text.}
\label{figure.sweeps-ql}
\end{figure*}

>>>>

These links enrich documents by connecting knowledge base information such as hyperlink graphs, entity membership in categories, and additional text to the annotated documents. In this paper, we explore one way in which information retrieval (IR) systems may use this data to improve the quality of search results. Unfortunately, producing high quality entity annotations is often a computationally expensive process. In addition, these systems generally require training data, which increases the barrier to use. Much entity linking and wikification research has also assumed more amenable circumstances that complicate their application to real-world text. For example, until 2014, the KBP entity linking track supplied explicit mention boundaries to participants.

@@

\noindent Like $P(q_i|D)$, we estimate $P(q_i|E)$ as a Dirichlet-smoothed query likelihood, but using the description text for entry $E$ in the knowledge base to estimate of the underlying model. By virtue of our entity-document scoring and normalization, we also have $P(E|D)$.

\begin{figure*}[!htb]
\centering
\begin{subfigure}{\columnwidth}
\centering
\includegraphics[width=.9\columnwidth]{figures/sweep-entities-AP.pdf}
\end{subfigure}%
\begin{subfigure}{\columnwidth}
\centering
\includegraphics[width=.9\columnwidth]{figures/sweep-entities-robust.pdf}
\end{subfigure}
%\begin{subfigure}{.5\columnwidth}
%\centering
%\includegraphics[width=\columnwidth]{figures/sweep-stanbol.pdf}
%\caption{Stanbol}
%\end{subfigure}
\caption{Sweeps over values of $\lambda$ for AP (a) and robust (b) \textit{kb} runs. $\lambda=0.0$ is equivalent to the baseline run.}
\label{figure.sweeps-ql}
\end{figure*}
